---
title: "Developing Data Products - Week 3 - Peer Assessment"
author: "b m g"
date: "6/17/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Objectives

* Create a webpage presentation using 
    + Menu, *File / New File/ R Markdown / Presentation (ioslides)*
    + Not Menu, *File / New File / R Presentation*
* Include a Plotly plot on one of the slides
* Host the Presentation on a webpage 
    + Here we will use (GitHub Pages) 
    + Be sure to include the creation date
* The data set Diamonds is used

## Loading Libraries and Data

* Library *plotly* is loaded
* data set *diamonds* is loaded

```{r, echo = FALSE, message=FALSE}
library(plotly)
data("diamonds")
```

## Plotly plot of selection of Diamond data
- *Carat* is independent variable (X), *price* dependent (Y), point size depends on *carat* variable and point color depends on color with cut quality used as third (Z) vatiable.

```{r, echo = FALSE, message=FALSE}
set.seed(150)
d <- diamonds[sample(nrow(diamonds), 500), ]
plot_ly(d, x = ~carat, y = ~price, z = ~cut, type = 'scatter3d', color = ~color,
        size = ~carat, text = ~paste("Clarity: ", clarity), mode='markers')
```

## References

- https://plot.ly/r/reference/#scatter
- Diamond data , http://ggplot2.tidyverse.org/reference/diamonds.html
- https://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf
- For more info on R Markdown presentation see <http://rmarkdown.rstudio.com>.
